---
title: "Product Pricing Algorithm"
author: "Alexei Domorev"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
    theme: flatly
params:
  interactive: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%")
```

```{r}
library(tidyverse) # LOADING LIBRARIES
library(tidyquant)
library(parsnip)
library(plotly)
```

```{r}
source("../00_scripts/separate_bikes_and_outlier_detection.R")
source("../00_scripts/plot_product_recommendation.R")
```

```{r}
bike_orderlines_tbl <- read_rds("../00_data/bike_sales/data_wrangled/bike_orderlines.rds")
```

```{r}
models_tbl <- read_rds("../00_models/parsnip_models_tbl.rds")
```

## Problem Statement

Research and Development wants help to determine new product ideas and pricing using existing product line as a benchmark.

## Solution Summary

We've identified several product gaps in the existing product line including:

1. Aluminum Over Mountain

2. Aluminum Triathlon

The Data Science team has developed a pricing model that uses predictive analytics to estimate the price of the new bicycle models based on the existing fleet. This ensures that new models are priced comparatively o other similar bicycles.

New product prediction for two new models:


1. Trigger, Over Mountain with Aluminum Frame: $3,265

2. Slice, Triathlon with Aluminum Frame: $2, 677

__Next Steps:__ Integrate the model into a proof-of-concept web application that can be deployed to the R&D Department.


## Gap Analysis

### Bike List

Our current product portfolio consists of 97 bike models that were analysed.

```{r}
get_bike_features()
```

### Gaps

The visualisation segments the full bicycle product line by category and frame material. 
This exposes two product gaps or opportunities for new products:

1. New __Aluminum__ line of bikes in the __Over Mountain__ category
2. New __Aluminum__ line of bikes in the __Triathlon__ category

```{r, out.height="600px"}
plot_bike_features(interactive = params$interactive)
```

\newpage
## Price Prediction

New product prediction for the two new models:

1. Trigger, Over Mountain with Aluminum Frame: $3,265;

2. Slice, Triathlon with Aluminum Frame: $2, 677.

```{r create-new-models}
# CREATE NEW MODELS
new_over_mountain_trigger <- tibble(
    model = "Trigger Al 1",
    frame_material = "Aluminum",
    category_2 = "Over Mountain",
    model_base = "Trigger",
    model_tier = "Aluminum 1",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_triathalon_slice_tbl <- tibble(
    model = "Slice Al 1",
    frame_material = "Aluminum",
    category_2 = "Triathalon",
    model_base = "Slice",
    model_tier = "Ultegra",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_bikes_tbl <- bind_rows(new_over_mountain_trigger, 
                           new_triathalon_slice_tbl)

# new_bikes_tbl
```

```{r}
# GET XGBOOST MODEL

models_tbl %>% 
    filter(model_id %>% str_detect("RF_RANDOMFOREST")) %>% 
    pull(model) %>% 
    pluck(1) -> # grabs the first element of the list
    model_best
    

```

```{r}
# OUTPUT PREDICTIONS IN A TABLE

model_best %>% 
    predict(new_bikes_tbl) %>% 
    mutate(.pred = scales::dollar(.pred, accuracy = 1)) %>% # accuracy = 1
    bind_cols(new_bikes_tbl) %>% 
    mutate(across(where(is.double), as.character)) %>% 
    rename(prediction = .pred) %>% 
    pivot_longer(cols = -model,
                 names_to = "New Model Attribute",
                 values_to = "value") %>% 
    pivot_wider(id_cols = "New Model Attribute", 
                names_from = model,
                values_from = value) %>% 
    knitr::kable(format = "pandoc", 
                 align = c("r", "l", "l"), 
                 caption = "Price Prediction", 
                 booktabs = TRUE,
                 escape = TRUE)

```


