---
title: "Customer Segmentation"
author: "Business Science"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
    theme: flatly
params:
  interactive: FALSE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%",
    fig.align = "center")
```

```{r}
library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel)
library(plotly)
```

```{r}
bike_orderlines_tbl <- read_rds("../00_data/bike_sales/data_wrangled/bike_orderlines.rds")
```

```{r}
source("../00_scripts/plot_customer_segmentation.R")
```


## Problem Statement

Marketing would like to increase email campaign engagement by segmenting the customer-base using their buying habits. 

## Solution Summary

The Data Science team has identified four customer segments. The segments were given descriptions based on the top product purchases within the segment.

1. __Segment 1 Preferences:__ Mountain Bikes, Above $3,200 (Premium Models)

2. __Segment 2 Preferences:__ Road Bikes, Above $3,200 (Premium Models)

3. __Segment 3 Preferences:__ Road Bikes, Below $3,200 (Economical Models)

4. __Segment 4 Preferences:__ Both Road and Mountain, Below $3,200 (Economical Models)


## Customer Preferences

### Heat Map

Our customer base consists of 30 bike shops. Based on the proportion of bikes purchased by category_1 and category_2, we can observe that several customers have strong preferences for Road or Mountain Bikes 

```{r, fig.height=12}
# PLOT CUSTOMER HEAT MAP
plot_customer_heatmap(interactive = params$interactive)
```

### Customer Segmentation

This is a 2D projection based on customer similarity that exposes four clusters, which are key segments in the customer base.

```{r, fig.height=5, fig.width=7}
# PLOT CUSTOMER SEGMENTS
plot_customer_segments(k = 4, seed = 123, interactive = params$interactive)
```


### Customer Preferences by Segment

The four customer segments were given descriptions based on the top product purchases within the segment.

1. __Segment 1 Preferences:__ Mountain Bikes, Above $3,200 (Premium Models)

2. __Segment 2 Preferences:__ Road Bikes, Above $3,200 (Premium Models)

3. __Segment 3 Preferences:__ Road Bikes, Below $3,200 (Economical Models)

4. __Segment 4 Preferences:__ Both Road and Mountain, Below $3,200 (Economical Models)

```{r, fig.height=8}
# PLOT CUSTOMER BEHAVIOR
plot_customer_behavior_by_cluster(top_n_products = 5, k = 4, seed = 123, interactive = params$interactive)
```

